---
title: "Multi-Omics Sleep Disorder Breathing"
author: "Nuzulul Kurniansyah & Tamar Sofer "
date: "12/29/2021"
output: 
  md_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This repository provides information and instruction how to perform the analysis in the manuscripts Multi-omics analysis of sleep-disorder sleeping traits across multiple blood tissues.

Second, this repository also provides the codes the we used for the analyses (see folder "Code"). 

## Required packages

We used [PRSice 2.3.1.e](https://www.prsice.info "PRSice 2.3.1.e") to generate PRS. We provide example code that also uses PRSice to construct PRS based on the provided summary statistics in folder "Summary_Statistics_for_PRS_construction".

Other software and packages that we used, but may not be necessary for others to construct the PRS, are as follows: \
1. We performed the analysis using R version 4.0.2.\
2. We used the following packages from CRAN: dplyr, tidyverse, data.table, purrr, pROC.\
3. We used the following packages from BioConductor: GENESIS, GWASTools.\

```{r eval=FALSE, echo=TRUE}

install.packages("dplyr")
library(dplyr)
library(bigsnpr)

```
